A Simple Model of Energy Transition Under a Carbon Budget

### 2015-04-26 DraftApril2715.tex
Formatted Results

\documentclass[singlespace]{easychithesis}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amssymb}
\newcommand{\Lagr}{\mathcal{L}}
\usepackage{tabulary}

@@

\begin{equation}
k^h(t) = H_0 e^{-t/n} + \int_0^t e^{x-t/n} H^+(x) dx - \int_0^t H^-(x)dx \geq 0 \qquad \forall t
\end{equation}

\begin{equation}
k^l(t) = L_0 e^{-t/n} + \int_0^t e^{x-t/n} L^+(x) dx - \int_0^t L^-(x)dx \geq 0 \qquad \forall t
\end{equation}

@@

\begin{equation}
C(H^+(t), L^+(t)) = \int_0^N (H^+(t) + L^+(t))e^{-rt}) dt \quad if H(t), L(t) \geq 0
\end{equation}

@@

\begin{equation}
G(t) = F^h(t) k^h(t) + F^l(t) k^l(t)
\end{equation}

@@

\begin{equation}
E_{max} = \alpha \int_0^N m^h(t) F^h(t) H^+(0) + m^l(t) F^l(t) L^+(0) dt \qquad \alpha \in [0,1]
\end{equation}

@@

\begin{equation}
E(H, L) = \int_0^N  m^h(t) F^h(t) H_0 + m^l(t) F^l(t) L_0 dt
\end{equation}

@@

\begin{equation}
E(H,L) \leq E_{max}
\end{equation}

@@

\begin{equation}
C = \int_0^N (H^+(t) + L^+(t))e^{-rt} dt
\end{equation}

@@

\begin{multline}
G = \bar{F}^h\left (H_0 e^{-t/n} + \int_0^t e^{x-t/n} H^+(x) dx - \int_0^t H^-(x)dx \right) \\ + \bar{F}^l(1-e^{-t/\tau}) \left ( L_0 e^{-t/n} + \int_0^t e^{x-t/n} L^+(x) dx - \int_0^t L^-(x)dx\right )
\end{multline}

\begin{equation}
\bar{E} \geq \int_0^N  \tilde{m}^h \bar{F}^h\left (H_0 e^{-t/n} + \int_0^t e^{x-t/n} H^+(x) dx - \int_0^t H^-(x)dx \right) dt
\end{equation}

\begin{equation}
H_0 e^{-t/n} + \int_0^t e^{x-t/n} H^+(x) dx - \int_0^t H^-(x)dx \geq 0 
\end{equation}

\begin{equation}
L_0 e^{-t/n} + \int_0^t e^{x-t/n} L^+(x) dx - \int_0^t L^-(x)dx \geq 0 
\end{equation}

\begin{equation}
H^+(t), H^-(t), L^+(t), L^-(t) \geq 0
\end{equation}

@@

\begin{equation}
\frac{d\Lagr}{dH^+(t)} = 1/r(e^{-rN} -1) + n(1-e^{-t/n})(\rho - \lambda F^h -\mu m F^h) + \sigma = 0
\end{equation}

\begin{equation}
\frac{d\Lagr}{dH^-(t)} = (\lambda F^h +\mu m F^h - \rho)t + \phi = 0
\end{equation}

\begin{equation}
\frac{d\Lagr}{dH^+(t)} = 1/r(e^{-rN} -1) + n(1-e^{-t/n})(\pi - \lambda F^l(1-e^{-t/\tau})) + \gamma = 0
\end{equation}

\begin{equation}
\frac{d\Lagr}{dH^-(t)} = (\lambda F^l(1-e^{-t/\tau}) - \pi)t + \delta = 0
\end{equation}

\begin{multline}
\frac{d\Lagr}{d\lambda} = G - F^h\left[nH^+(t) + e^{-t/n}(n^2 + H_0(1-n)) - n^2 + \int_0^tH^-(x)dx\right] \\ - F^l (1-e^{-t/\tau})\left[nL^+(t) + e^{-t/n}(n^2 + L_0(1-n)) - n^2 + \int_0^tL^-(x)dx\right] = 0
\end{multline}

\begin{multline}
\frac{d\Lagr}{d\mu} = \bar{E} - mF^h \left [(1-e^{-N/n})(1-n)H_0 n + n^2(N + n(1-e^{-N/n})) \right.\\ + \left. n\int_0^N H^+(t) dt - \int_0^N\int_0^t H^-(x)dx dt   \right] \geq 0
\end{multline}

\begin{equation}
\frac{d\Lagr}{d\rho} = H_0 e^{-t/n}(1-n) + nH^+(t) - n^2(1-e^{-t/n}) - \int_0^t H^-(x)dx \geq 0 
\end{equation}

\begin{equation}
\frac{d\Lagr}{d\pi} = L_0 e^{-t/n}(1-n) + nL^+(t) - n^2(1-e^{-t/n}) - \int_0^t L^-(x)dx \geq 0 
\end{equation}

@@

\begin{tabulary}{1.0\textwidth}{LLLL}
    Variable & Description & Value & Source\\
    \hline
alpha &  Regional Land Area  &  Not Specified  &  N/A \\
area0 &  Initial Regional Land Area  &  Not Specified  &  N/A \\
landloss &  Regional Land Loss due to Sea Level Rise  &  Not Specified  &  N/A \\
	\hline
\end{tabulary}

@@

\includegraphics[width=0.9\textwidth]{cap_and_invest_results_A_1.png}
\includegraphics[width=0.9\textwidth]{cap_and_invest_results_A_25.png}

\includegraphics[width=0.9\textwidth]{cap_and_invest_results_A_50.png}

\includegraphics[width=0.9\textwidth]{cap_and_invest_results_A_75.png}
\includegraphics[width=0.9\textwidth]{cap_and_invest_results_A_100.png}

\includegraphics[width=0.9\textwidth]{cap_and_invest_results_Fl_1.png}
\includegraphics[width=0.9\textwidth]{cap_and_invest_results_Fl_25.png}
\includegraphics[width=0.9\textwidth]{cap_and_invest_results_Fl_50.png}
\includegraphics[width=0.9\textwidth]{cap_and_invest_results_Fl_75.png}
\includegraphics[width=0.9\textwidth]{cap_and_invest_results_Fl_100.png}

\includegraphics[width=0.9\textwidth]{cost_as_func_of_Fl_emissions_05.png}

\includegraphics[width=0.9\textwidth]{cost_as_func_of_Alpha.png}

>>>>

\documentclass[singlespace]{easychithesis}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amssymb}
\newcommand{\Lagr}{\mathcal{L}}
\usepackage{tabulary}
\usepackage{float}
\floatstyle{boxed}
\restylefloat{figure}
\usepackage[section]{placeins}

@@

\begin{equation}\label{eq:simpleHCapitalConstraint}
k^h(t) = H_0 e^{-t/n} + \int_0^t e^{x-t/n} H^+(x) dx - \int_0^t H^-(x)dx \geq 0 \qquad \forall t
\end{equation}

\begin{equation}\label{eq:simpleLCapitalConstraint}
k^l(t) = L_0 e^{-t/n} + \int_0^t e^{x-t/n} L^+(x) dx - \int_0^t L^-(x)dx \geq 0 \qquad \forall t
\end{equation}

@@

\begin{equation}\label{eq:simpleObjective}
C(H^+(t), L^+(t)) = \int_0^N (H^+(t) + L^+(t))e^{-rt}) dt \quad if H(t), L(t) \geq 0
\end{equation}

@@

\begin{equation}\label{eq:simpleGenConstraint}
G(t) = F^h(t) k^h(t) + F^l(t) k^l(t)
\end{equation}

@@

\begin{equation}\label{eq:simpleMaxEmission}
E_{max} = \alpha \int_0^N m^h(t) F^h(t) H^+(0) + m^l(t) F^l(t) L^+(0) dt \qquad \alpha \in [0,1]
\end{equation}

@@

\begin{equation}\label{eq:simpleSimEmission}
E(H, L) = \int_0^N  m^h(t) F^h(t) H_0 + m^l(t) F^l(t) L_0 dt
\end{equation}

@@

\begin{equation}\label{eq:simpleEmitConstraint}
E(H,L) \leq E_{max}
\end{equation}

@@

\begin{equation}\label{eq:analyticalObj}
C = \int_0^N (H^+(t) + L^+(t))e^{-rt} dt
\end{equation}

@@

\begin{multline}\label{eq:analyticalGen}
G = \bar{F}^h\left (H_0 e^{-t/n} + \int_0^t e^{x-t/n} H^+(x) dx - \int_0^t H^-(x)dx \right) \\ + \bar{F}^l(1-e^{-t/\tau}) \left ( L_0 e^{-t/n} + \int_0^t e^{x-t/n} L^+(x) dx - \int_0^t L^-(x)dx\right )
\end{multline}

\begin{equation}\label{eq:analyticalEmit}
m^hF^h\left (H_0 e^{-t/n} + \int_0^t e^{x-t/n} H^+(x) dx - \int_0^t H^-(x)dx \right) \leq \alpha N m^h F^h H^+(0)
\end{equation}

\begin{equation}\label{eq:analyticalHCapConstraint}
H_0 e^{-t/n} + \int_0^t e^{x-t/n} H^+(x) dx - \int_0^t H^-(x)dx \geq 0 
\end{equation}

\begin{equation}\label{eq:analyticalLCapConstraint}
L_0 e^{-t/n} + \int_0^t e^{x-t/n} L^+(x) dx - \int_0^t L^-(x)dx \geq 0 
\end{equation}

\begin{equation}\label{eq:analyticalDecisionVarConstraint}
H^+(t), H^-(t), L^+(t), L^-(t) \geq 0
\end{equation}

@@

\begin{equation}\label{eq:dLdH+}
\frac{d\Lagr}{dH^+(t)} = 1/r(e^{-rN} -1) + n(1-e^{-t/n})(\rho - \lambda F^h -\mu m F^h) + \sigma = 0
\end{equation}

\begin{equation}\label{eq:dLdH-}
\frac{d\Lagr}{dH^-(t)} = (\lambda F^h +\mu m F^h - \rho)t + \phi = 0
\end{equation}

\begin{equation}\label{eq:dLdL+}
\frac{d\Lagr}{dH^+(t)} = 1/r(e^{-rN} -1) + n(1-e^{-t/n})(\pi - \lambda F^l(1-e^{-t/\tau})) + \gamma = 0
\end{equation}

\begin{equation}\label{eq:dLdL-}
\frac{d\Lagr}{dH^-(t)} = (\lambda F^l(1-e^{-t/\tau}) - \pi)t + \delta = 0
\end{equation}

\begin{multline}\label{eq:dLdlambda}
\frac{d\Lagr}{d\lambda} = G - F^h\left[nH^+(t) + e^{-t/n}(n^2 + H_0(1-n)) - n^2 + \int_0^tH^-(x)dx\right] \\ - F^l (1-e^{-t/\tau})\left[nL^+(t) + e^{-t/n}(n^2 + L_0(1-n)) - n^2 + \int_0^tL^-(x)dx\right] = 0
\end{multline}

\begin{multline}\label{eq:dLdmu}
\frac{d\Lagr}{d\mu} = \bar{E} - mF^h \left [(1-e^{-N/n})(1-n)H_0 n + n^2(N + n(1-e^{-N/n})) \right.\\ + \left. n\int_0^N H^+(t) dt - \int_0^N\int_0^t H^-(x)dx dt   \right] \geq 0
\end{multline}

\begin{equation}\label{eq:dLdrho}
\frac{d\Lagr}{d\rho} = H_0 e^{-t/n}(1-n) + nH^+(t) - n^2(1-e^{-t/n}) - \int_0^t H^-(x)dx \geq 0 
\end{equation}

\begin{equation}\label{eq:dLdpi}
\frac{d\Lagr}{d\pi} = L_0 e^{-t/n}(1-n) + nL^+(t) - n^2(1-e^{-t/n}) - \int_0^t L^-(x)dx \geq 0 
\end{equation}

@@

\begin{tabulary}{1.0\textwidth}{LLLL}
Variable & Description & Value & Source\\
\hline
$\alpha$ &  \% Business As Usual Emissions  &  Varied  &  Varied \\
$Fl_min$ & & & \\
$F_max$ & & & \\
$Scale$ & & & \\
$Fh_min$ & & & \\
$Fh_max$ & & & \\
$G_0$ & & & \\
$G_m$ & & & \\
$c^l$ & & & \\
$c^h$ & & & \\
\hline
\end{tabulary}

@@

\section{Model Results}
\FloatBarrier

\begin{figure}[h]\label{fig:SimpleResultsA=1}
\includegraphics[width=\textwidth]{cap_and_invest_results_A_1.png}
\caption{Alpha = 1}
\end{figure}

\begin{figure}[h]\label{fig:SimpleResultsA=25}
\includegraphics[width=\textwidth]{cap_and_invest_results_A_25.png}
\caption{Alpha = 25}
\end{figure}

\begin{figure}[h]\label{fig:SimpleResultsA=50}
\includegraphics[width=\textwidth]{cap_and_invest_results_A_50.png}
\caption{Alpha = 50}
\end{figure}

\begin{figure}[h]\label{fig:SimpleResultsA=75}
\includegraphics[width=\textwidth]{cap_and_invest_results_A_75.png}
\caption{Alpha = 75}
\end{figure}

\begin{figure}[h]\label{fig:SimpleResultsA=100}
\includegraphics[width=\textwidth]{cap_and_invest_results_A_100.png}
\caption{Alpha = 100}
\end{figure}

\begin{figure}[h]\label{fig:SimpleResultsFl=1}
\includegraphics[width=\textwidth]{cap_and_invest_results_Fl_1.png}
\caption{Fl = 1}
\end{figure}

\begin{figure}[h]\label{fig:SimpleResultsFl=25}
\includegraphics[width=\textwidth]{cap_and_invest_results_Fl_25.png}
\caption{Fl = 25}
\end{figure}

\begin{figure}[h]\label{fig:SimpleResultsFl=50}
\includegraphics[width=\textwidth]{cap_and_invest_results_Fl_50.png}
\caption{Fl = 50}
\end{figure}

\begin{figure}[h]\label{fig:SimpleResultsFl=75}
\includegraphics[width=\textwidth]{cap_and_invest_results_Fl_75.png}
\caption{Fl = 75}
\end{figure}

\begin{figure}[h]\label{fig:SimpleResultsFl=100}
\includegraphics[width=\textwidth]{cap_and_invest_results_Fl_100.png}
\caption{Fl = 100}
\end{figure}

\begin{figure}[h]\label{fig:costVsFl}
\includegraphics[width=\textwidth]{cost_as_func_of_Fl_emissions_05.png}
\caption{Cost vs Fl}
\end{figure}

\begin{figure}[h]\label{fig:costVsAlpha}
\includegraphics[width=\textwidth]{cost_as_func_of_Alpha.png}
\caption{Cost vs Alpha}
\end{figure}

\FloatBarrier
